---
title: "REVIEW & DESCRIPTIVE STATISTICS WITH R"
---

Goal: We will cover various R commands for descriptive statistics.
Data: iraq.csv

1.	Exploring the Iraq data.
(a)	How many records (observations) are in the data set?
```{r}
length(iraq$Obs.Number)
```
(b)	How many variables are in the data set?
```{r}
length(names(iraq))
```
2.  For the Age variable in the Iraq data, calculate the
(a)	Mean: 			_________
(b)	Median:		__________
(c)	Standard deviation:	__________
(d)	Maximum:		__________
(e)	IQR:			___________
```{r}
mean(iraq$Age,na.rm=T)
```
```{r}
median(iraq$Age,na.rm=T)
```
```{r}
sd(iraq$Age,na.rm=T)
```
```{r}
max(iraq$Age,na.rm=T)
```
```{r}
IQR(iraq$Age,na.rm=T)
```

3.	For the Hometown variable:
Which hometown had the largest number of casualties in the data?   How many?  (Hint: The sort() function can be useful for ordering the values that come out of the table() function…)  (Houston-34)
```{r}
fivenum(sort(table(iraq$Hometown[iraq$Hometown!="Not reported yet"])))
```
4.	 Create and attach a frequency histogram and a boxplot of Age only for those with Rank of "Corporal."  Appropriately label the x- and y-axes, and further modify the plots as desired to make them look professional.  Hint: use iraq$Age[iraq$Rank=="Corporal"] to get the needed ages.
```{r}
hist(iraq$Age[iraq$Rank=="Corporal"], xlab="Age of Corporal's", ylab="Frequency")
```
```{r}
boxplot(iraq$Age[iraq$Rank=="Corporal"], ylab = "Age of Corporal's", main="Boxplot")
```
